---
output:
  github_document:
    md_extensions: -smart
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# biostatlab

`biostatlab` is an R data package for biostatistics labs and modelling
benchmarks. It stores curated datasets as package data and exposes a registry
that groups tasks into survival, classification, and regression workflows.

## Usage

```r
library(biostatlab)

dataset_registry()
datasets_by_task("survival")
heart_failure <- load_dataset("heart_failure")
```

Each dataset has a documentation page with dimensions, task type, target
columns, and references when available.


## Tutorial Template

Create a new tutorial from the package template:

```r
rmarkdown::draft(
  "my-tutorial.Rmd",
  template = "biostatlab_tutorial",
  package = "biostatlab",
  create_dir = TRUE
)
```

This template keeps the layout stable and applies a light, elegant visual style.

Create a beamer slide deck with:

```r
rmarkdown::draft(
  "slides.Rmd",
  template = "biostatlab_beamer",
  package = "biostatlab",
  create_dir = TRUE
)
```

The beamer template keeps the native look, widens the content area, and switches bullet markers to circles.

## Available Datasets

```{r available-datasets, echo = FALSE}
load("data/biostatlab_registry.rda")

outcome_columns <- Map(
  function(task, target, time, event) {
    if (identical(task, "survival")) {
      unique(stats::na.omit(c(time, event)))
    } else {
      target
    }
  },
  biostatlab_registry$task,
  biostatlab_registry$target,
  biostatlab_registry$time,
  biostatlab_registry$event
)

readme_registry <- data.frame(
  Dataset = paste0("`", biostatlab_registry$name, "`"),
  Task = biostatlab_registry$task,
  Outcome = ifelse(
    biostatlab_registry$task == "survival",
    paste0("`Surv(", biostatlab_registry$time, ", ", biostatlab_registry$event, ")`"),
    paste0("`", biostatlab_registry$target, "`")
  ),
  Predictors = paste0(biostatlab_registry$n_columns - lengths(outcome_columns), " columns"),
  Source = biostatlab_registry$reference,
  Title = biostatlab_registry$title,
  check.names = FALSE
)

knitr::kable(readme_registry)
```
