---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# biostatlab

`biostatlab` is an R data package for biostatistics labs and modelling
benchmarks. It stores curated datasets as package data and exposes a registry
that groups tasks into survival, classification, and regression workflows.

## Usage

```r
library(biostatlab)

dataset_registry()
datasets_by_task("survival")
heart_failure <- load_dataset("heart_failure")
```

Each dataset has a documentation page with dimensions, task type, target
columns, and references when available.

## Available Datasets

```{r available-datasets, echo = FALSE}
load("data/biostatlab_registry.rda")

readme_registry <- biostatlab_registry[, c("name", "task", "target", "title")]
names(readme_registry) <- c("Dataset", "Task", "Target", "Title")
readme_registry$Dataset <- paste0("`", readme_registry$Dataset, "`")
readme_registry$Target <- paste0("`", readme_registry$Target, "`")

knitr::kable(readme_registry)
```
